Accurate Measurement of Bicycle Parameters

### 2010-10-19 papers/BMD2010/PhysicalParametersPoster/poster.tex
fixed the legend colors on the bode plot

\setbeamercolor{block title}{fg=ngreen,bg=white}
\setbeamercolor{block body}{fg=black,bg=white}
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70}
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10}

>>>>

\setbeamercolor{block title}{fg=ucdgold,bg=white}
\setbeamercolor{block body}{fg=black,bg=white}
\setbeamercolor{block alerted title}{fg=white,bg=ucdblue}
\setbeamercolor{block alerted body}{fg=black,bg=ucdblue!10}
